Self Regulation Ontology Retest Data Report

### 2017-11-03 code/SRO_Report.Rmd
cont cleaning report

@@

@@

In the model below (after the model comparison the interactive one is significantly better) the baseline is difference accuracy.

Main effects: Compared to this overall accuracy has higher reliability and difference threshold has lower reliability. Other difference parameters do not differ from difference accuracy significantly.

Interactions: Drift rates, thresholds are higher for overall than difference; response times are marginally so.

Conclusion: Overall parameter estimates are higher than difference estimates (except for non-decision time).

```{r}
summary(lm(icc ~ label_1*label_3,tmp))
```

Closer look at simple effects:

Are overall drift rates meaninfully higher than overall raw accuracies? Yes.

```{r}
tmp_simp = tmp %>%
  filter(label_3 %in% c("drift rate", "accuracy"),
         label_1 == 'overall')

summary(lm(icc~label_3, tmp_simp))
```

Are overall drift rates meaninfully higher than overall raw response times? No, not worse either.

```{r}
tmp_simp = tmp %>%
  filter(label_3 %in% c("drift rate", "rt"),
         label_1 == 'overall')

summary(lm(icc~label_3, tmp_simp))
```

Are overall thresholds meaninfully higher than overall raw accuracies? No, not worse either.

```{r}
tmp_simp = tmp %>%
  filter(label_3 %in% c("threshold", "accuracy"),
         label_1 == 'overall')

summary(lm(icc~label_3, tmp_simp))
```

Are overall thresholds meaninfully higher than overall raw response times? No, they are worse.

```{r}
tmp_simp = tmp %>%
  filter(label_3 %in% c("threshold", "rt"),
         label_1 == 'overall')

summary(lm(icc~label_3, tmp_simp))
```

Are overall non-decision times meaninfully higher than overall raw accuracies? No, not worse either.

```{r}
tmp_simp = tmp %>%
  filter(label_3 %in% c("non-decision", "accuracy"),
         label_1 == 'overall')

summary(lm(icc~label_3, tmp_simp))
```

Are overall non-decision times meaninfully higher than overall raw response times? No, they are worse.

```{r}
tmp_simp = tmp %>%
  filter(label_3 %in% c("non-decision", "rt"),
         label_1 == 'overall')

summary(lm(icc~label_3, tmp_simp))
```

@@

<a id="diff_plot"></a>
For reference here are the box plots showing the distribution of difference scores for each task.

```{r warning=FALSE, message=FALSE, fig.height=36}
t1_2_difference %>%
           ggplot(aes(reorder(dv, difference, FUN=median), difference))+
           geom_hline(yintercept = 0,color='red',size=1)+
           geom_boxplot()+
           theme_bw()+
           xlab("")+
           ylab("Standardized difference")+
           coord_flip()
```

@@

Distributions of bootstrapped reliabilities. Yellow points are where our point estimates fall from the retest sample. Surveys are filled in red but can't be seen because the variance around their bootstrapped ICC's is very low.

```{r fig.height=36}
 boot_df %>%
  mutate(task = ifelse(grepl("survey",dv), "survey","task")) %>%
  ggplot(aes(reorder(dv, icc, FUN=var), icc, fill = task))+
  geom_boxplot()+
  geom_hline(yintercept = 0,color='red',size=1)+
  geom_point(data = rel_df, aes(x=dv, y = icc),  color = "yellow")+
  theme_bw()+
  theme(legend.title = element_blank())+
  xlab("")+
  coord_flip()
```

@@

```{r}
boot_df = boot_df %>%
    mutate(task = ifelse(grepl("survey",dv), "survey","task"))

@@

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'task') %>%
  select(-measure_description, -notes, -measure_type, -task) %>%
  # left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
  separate(variable_type, c("label_1", "label_2", "label_3"), sep = ",") %>%
  mutate(label_1 = trim(label_1),
         label_2=trim(label_2),
         label_3=trim(label_3))%>%
  filter(ddm_task == 1) %>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.', remove=FALSE) %>%
  select(-extra_1, -extra_2) %>%
  drop_na() %>%
  left_join(boot_df[,c("dv", "icc")], by = 'dv')
```

```{r}
summary(lmerTest::lmer(icc ~ label_1*label_3 + (1|dv) ,tmp))
```

>>>>

Plot the distributions of different types of variables

```{r warning=FALSE, message=FALSE}
measure_labels %>%
  select(dv, task, variable_type, ddm_task, num_all_trials)%>%
  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
  filter(task == "task") %>%
  select(-var, -task) %>%
  left_join(rel_df[,c("dv", "icc")], by="dv")%>%
  # filter(ddm_task == 1) %>%
  separate(variable_type, c("overall_difference", "raw_EZ_hddm", "param"), extra="merge") %>%
  mutate(raw_EZ_hddm = ifelse(ddm_task == 0, "other", raw_EZ_hddm),
         param = ifelse(ddm_task == 0, "other", param)) %>%
  na.omit() %>%
  filter(overall_difference!='condition') %>%
  ggplot(aes(x=factor(raw_EZ_hddm, levels = c("raw", "EZ", "hddm", "other"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion", "Other")),y=icc,fill=param))+
  geom_boxplot(position = position_dodge(width=0.75))+
  facet_wrap(~factor(overall_difference, levels=c("overall", "difference"), labels=c("Overall", "Difference")))+
  theme_bw()+
  xlab("")+
  ylab("ICC")+
  theme(legend.title = element_blank())
```

@@

Reliabilities for difference variables is lower.

@@

When all trials are used the drift rates and rt's have higher reliabilities compared to accuracies.

```{r}
summary(lm(icc~label_3,tmp[tmp$label_1=="overall",]))
```

@@

@@

@@

```{r}
boot_df = boot_df %>%
    mutate(task = ifelse(grepl("survey",dv), "survey","task"),
           task = ifelse(grepl("holt",dv), "task", task))

@@

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'task') %>%
  separate(variable_type, c("label_1", "label_2", "label_3"), sep = ",") %>%
  mutate(label_1 = trim(label_1),
         label_2=trim(label_2),
         label_3=trim(label_3))%>%
  filter(ddm_task == 1) %>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.', remove=FALSE) %>%
  select(-extra_1, -extra_2) %>%
  drop_na() %>%
  left_join(boot_df[,c("dv", "icc")], by = 'dv')
```

```{r}
summary(lmerTest::lmer(icc ~ label_1 + (1|dv) ,tmp))
```

```{r}
summary(lmerTest::lmer(icc ~ label_3 + (1|dv) ,tmp))
```

```{r warning=FALSE, message=FALSE}
poster_vars <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/poster_var_list.csv', header=F)

names(poster_vars) = "var"

boot_df_poster = boot_df[boot_df$dv %in% poster_vars$var,]

boot_df_poster = boot_df_poster%>%
  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
  separate(var, c("var"), sep="\\.",remove=TRUE,extra="drop") %>%
  mutate(task_group = gsub("_", " ", task_group),
         var = gsub("_", " ", var)) %>%
  arrange(task_group, var)

boot_df_poster = boot_df_poster %>%
  left_join(rel_df[,c("dv", "icc")], by = "dv") %>%
  rename(icc = icc.x, point_est = icc.y)

#Manual correction
boot_df_poster = boot_df_poster %>%
  mutate(task = ifelse(task_group == 'holt laury survey', "task", task)) %>%
  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
  mutate(task_group = gsub("survey", "", task_group))
```

```{r warning=FALSE, message=FALSE} 
p4 <- boot_df_poster %>%
  filter(task == 'task') %>%
ggplot(aes(y = var, x = icc)) + 
  geom_point(color = '#00BFC4')+
  geom_point(aes(y = var, x = point_est), color = "black")+
  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y", labeller = label_wrap_gen(width=20)) +
  theme(panel.spacing = unit(0.75, "lines"), 
        strip.placement = "outside",
        strip.text.y = element_text(angle=180, size=36),
        axis.text.y = element_text(size=20),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey80")) + 
  xlab("")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_y_discrete(labels = function(x) str_wrap(x, width = 10))+
  scale_shape_manual(breaks = sort(boot_df_poster$type), values = c(15, 17, 3))+
  geom_vline(xintercept = 0, color = "red", size = 1)

p5 <- boot_df_poster %>%
  filter(task == 'survey') %>%
ggplot(aes(y = var, x = icc)) + 
  geom_point(color = '#F8766D')+
  geom_point(aes(y = var, x = point_est), color = "black")+
  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y", labeller = label_wrap_gen(width=20)) +
  theme(panel.spacing = unit(0.75, "lines"), 
        strip.placement = "outside",
        strip.text.y = element_text(angle=180, size=36),
        axis.text.y = element_text(size=20),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey80")) + 
  xlab("")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_y_discrete(labels = function(x) str_wrap(x, width = 10))+
  scale_shape_manual(breaks = sort(boot_df_poster$type), values = c(15, 17, 3))+
  geom_vline(xintercept = 0, color = "red", size = 1)

p6 <- arrangeGrob(p4, p5,nrow=1)

ggsave('Bootstrap_Poster_Plot.jpg', plot = p6, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 24, height = 42, units = "in", limitsize = FALSE)
```

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/Bootstrap_Poster_Plot.jpg')
```

```{r echo=FALSE}
rm(p4, p5, p6)
```

```{r}
p4_t <- boot_df_poster %>%
  filter(task == 'task') %>%
ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc)) + 
  geom_violin(fill='#00BFC4')+
  theme_bw() + 
  theme(axis.text.y = element_text(size=30))+
  xlab("")+
  ylab("")+
  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 15))+
  geom_hline(yintercept = 0, color = "red", size = 1)+
  coord_flip()

p5_t <- boot_df_poster %>%
  filter(task == 'survey') %>%
ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc)) + 
  geom_violin(fill='#F8766D')+
  theme_bw() + 
  theme(axis.text.y = element_text(size=43))+
  xlab("")+
  ylab("")+
  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
  geom_hline(yintercept = 0, color = "red", size = 1)+
  coord_flip()

p6_t <- arrangeGrob(p4_t, p5_t,nrow=1)

ggsave('Bootstrap_Poster_Plot_t.jpg', plot = p6_t, device = "jpeg", path = "../output/figures/", width = 27, height = 48, units = "in", limitsize = FALSE)
```

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/Bootstrap_Poster_Plot_t.jpg')
```

```{r echo=FALSE}
rm(p4_t, p5_t, p6_t)
```
